### 2022-09-04 chapter5/chapter.tex
is it finished?? :o

%!TEX root = ../thesis.tex
\chapter{Global convergence results}\label{ch: global results}
In this chapter we prove convergence results which build on the main results of Chapter~\ref{sec: conv}. We consider the discrete-time embedded processes formed by observing the QBD-RAP at the orbit restart epochs and by observing the fluid queue at the hitting times of the level process at the on points \(\{y_\ell\}\), which are the boundaries of the intervals \(\{\calD_\ell\}\). In Corollary~\ref{cor: aln22222212} we prove that the transition probability of the embedded process of the QBD-RAP converge those of the embedded process of the fluid queue. In Corollary~\ref{cor: short cor} we prove that the distribution of the sojourn time of the QBD-RAP in a given level converges to the distribution of the sojourn time of the fluid queue in the corresponding interval. In Theorem~\ref{thm: big thm}, we state global results on the weak convergence (in space and time) of the QBD-RAP approximation scheme to the fluid queue.

@@

Consider the embedded process formed by observing the QBD-RAP at the orbit restart epochs. Let \(\{\tau_n^{(p)}\}_{n\geq 0, n \in \mathbb Z}\), \(\tau_0^{(p)}=0\), and
\[\tau_{n}^{(p)} = \inf\left\{t\geq \tau_{n-1}^{(p)} \mid L^{(p)}(t)\neq L^{(p)}(\tau_{n-1}^{(p)}), \mbox{or \(\{\bs Y(t)\}\) hits a boundary}\right\},\]
be orbit restart epochs. These are the (stopping) times at which the level process of the QBD-RAP, \(\{L^{(p)}(t)\}\), changes, or the boundary is hit, or, if the process is at the boundary, the process leaves the boundary. To simplify notation, we may drop the superscript \(p\) where it is not explicitly needed. Further, let \(\{\Ydp(n)\}_{n\geq 0, n \in \mathbb Z} = \{(L^{(p)}(\tau_n^{(p)}),\varphi(\tau_n^{(p)}))\}_{n\geq 0, n \in \mathbb Z}\) be the level and phase of the discrete-time process embedded at the orbit restart epochs, \(\{\tau_n^{(p)}\}_{n\geq 0}\). The subscript \(\bs \alpha \) refers to the fact that \(\bs A^{(p)}(\tau_n^{(p)})=\bs \alpha^{(p)}\) for \(n\geq 1\), unless the process is temporarily absorbed in a sticky boundary, in which case \(\bs A^{(p)}(\tau_n^{(p)})=1\). The process \(\{\Ydp(n)\}_{n\geq 0}\) is a discrete-time Markov chain, which is time-homogeneous for \(n\geq 1\).

@@

We have the following result on the convergence of the embedded processes \(\{\Ydp(n)\}\) and \(\{\bs X(\tau_n^X)\}\), which we also will utilise later to prove a global result.
\begin{cor}\label{cor: aln222222} For \(\ell_0\in\mathcal K,\) \(x_0\in\mathcal D_{\ell_0,i}\), \(i\in\mathcal S\), 
	for \(n=0\), then
	\begin{align}
		&\mathbb P(\Ydp(1) = (\ell(\ell_0,j),j), \tau_1^{(p)}\leq E^\lambda
            	 \mid \bs Y^{(p)}(0) = (\ell_0,\bs a_{\ell_0,i}^{(p)}(x_0),i)) \nonumber
	 	%
		\\&\to  
			\mathbb P(\bs X(\tau_1^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_1^{X}\leq E^\lambda \mid \bs X(0) = (x_0,i)),\label{eqn: lim 1}
	\end{align}
	and for \(n\geq 1\), 
	\begin{align}
		&\mathbb P(\Ydp(n+1) = (\ell(\ell_0,j),j), \tau_{n+1}^{(p)}\leq E^\lambda
            	 \mid \Ydp(n) = (\ell_0,i), \tau_n^{(p)}\leq E^\lambda) \nonumber
	 	%
		\\&\to  
			\mathbb P(\bs X(\tau_{n+1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_{n+1}^{X}\leq E^\lambda \mid \bs X(\tau_{n}^X) = (y_{\ell_0+1(i\in\calS_-)},i), \tau_n^{X}\leq E^\lambda).\label{eqn: ddddddd}
	\end{align}
	where \(\ell(\ell_0,j)\) can take values
	\begin{align}
		\ell(\ell_0,j) = \begin{cases}
			\ell_0-1, & \ell_0\in\{0,1,\dots,K+1\},\, j\in\calS_-\\
			%
			\ell_0, & \ell_0 = 0, j\in\mathcal S_+, \mbox{ or }\ell_0 = K, j\in\mathcal S_-,\\
			%
			\ell_0+1, & \ell_0\in\{-1,0,1,\dots,K\},\, j\in\calS_+.
		\end{cases}
	\end{align}
	% and 
	% \begin{align}
	% 	y(\ell,\ell_0,j) = \begin{cases}
	% 		y_{\ell_0}, & \ell=\ell_0-1,\, j\in\calS_-, \mbox{ or } \ell=\ell_0=0,\, j \in\calS_+, \\
	% 		y_{\ell_0+1}, & \ell=\ell_0+1,\, j\in\calS_+, \mbox{ or } \ell=\ell_0=K,\, j \in\calS_-.
	% 	\end{cases}
	% \end{align}
\end{cor}
\begin{proof}
The convergence for \(\ell_0\in\{-1,K+1\}\) holds trivially as the QBD-RAP and fluid queue have the same behaviour at the sticky boundary.

@@

All that is left is to prove (\ref{eqn: ddddddd}). For \(n\geq 1\), consider the transition probabilities of the embedded process from the QBD-RAP, 
\begin{align}
	&\mathbb P(\Ydp(n+1) = (\ell(\ell_0,j),j),\tau_{n+1}^{(p)}\leq E^\lambda
	\mid \Ydp(n) = (\ell_0,i),\tau_{n}^{(p)}\leq E^\lambda) \nonumber 
	\\&=\mathbb P(\Ydp(1) = (\ell(\ell_0,j),j), \tau_{1}^{(p)}\leq E^\lambda
	\mid \bs Y^{(p)}(0)=(\ell_0 ,\bs\alpha, i)), \label{eqn: aaannnn}
\end{align}
since the QBD-RAP is time-homogeneous and the exponential random variable \(E^\lambda\) is memoryless. %The probability on the right of (\ref{eqn: aaannnn}) is equal to
% \begin{align}
% 	&\mathbb P(L^{(p)}(\tau_1^{(p)}) = \ell_0-1(j\in\calS_-)+1(j\in\calS_+), \varphi(\tau_1^{(p)}) = j
% 			 \mid \bs Y^{(p)}(0) = (\ell_0 ,\bs\alpha, i)).\nonumber
% 	%  \intertext{for \(j\in\calS_+\)}
% 	%  &\mathbb P(L^{(p)}(\tau_1^{(p)}) = \ell_0-1, \varphi(\tau_1^{(p)}) = j
% 	% 		 \mid \bs Y^{(p)}(0) = \bs y_0^{(p)}) \nonumber
% \end{align}
% Thus, once again noting that \(\tau_1^{(p)}<\infty\) almost surely, then taking \(\lambda \to 0\) in 
Applying Corollary~\ref{cor: aln222} to (\ref{eqn: aaannnn}) then
\begin{align}
	&\mathbb P(\Ydp(n+1) = (\ell(\ell_0,j),j),\tau_{n+1}^{(p)}\leq E^\lambda
	\mid \Ydp(n) = (\ell_0,i),\tau_{n}^{(p)}\leq E^\lambda) \nonumber 
	\\&\to \mathbb P(\bs X(\tau_{1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_{1}^{X}\leq E^\lambda \mid \bs X(0) = (y_{\ell_0+1(i\in\calS_-)},i)).\label{eqnL sdfdfaaa}
\end{align}
Since the fluid queue is time-homogeneous, and \(E^\lambda\) memoryless, then (\ref{eqnL sdfdfaaa}) is equal to 
\begin{align}
	&\mathbb P(\bs X(\tau_{1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_{1}^{X}\leq E^\lambda \mid \bs X(\tau_{1}^X) = (y_{\ell_0+1(i\in\calS_-)},i)) \nonumber
	\\&=\mathbb P(\bs X(\tau_{n+1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_{n+1}^{X}\leq E^\lambda \mid \bs X(\tau_{n}^X) = (y_{\ell_0+1(i\in\calS_-)},i), \tau_{n}^{X}\leq E^\lambda ),
\end{align}
which proves the result. 
\end{proof}
A direct corollary of Corollary~\ref{cor: aln222222} is the convergence of the transition probabilities of the embedded process. 
\begin{cor}\label{cor: aln22222212} For \(\ell_0\in \mathcal K,\) \(x_0\in\mathcal D_{\ell_0,i}\), \(i\in\mathcal S\), 
		for \(n=0\), then
		\begin{align}
			&\mathbb P(\Ydp(1) = (\ell(\ell_0,j),j)
					 \mid \bs Y^{(p)}(0) = (\ell_0,\bs a_{\ell_0,i}^{(p)}(x_0),i)) \nonumber
			 %
			\\&\to  
				\mathbb P(\bs X(\tau_1^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j)  \mid \bs X(0) = (x_0,i)).\label{eqn: lim 2}
		\end{align}
		and for \(n\geq 1\),  
		\begin{align}
			&\mathbb P(\Ydp(n+1) = (\ell(\ell_0,j),j) 
					 \mid \Ydp(n) = (\ell_0,i) ) \nonumber
			 %
			\\&\to  
				\mathbb P(\bs X(\tau_{n+1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j) \mid \bs X(\tau_{n}) = (y_{\ell_0+1(i\in\calS_-)},i) ).\label{eqn: ddddddd2}
		\end{align}
\end{cor}
\begin{proof}
	Since \(\tau_1^{(p)}<\infty\) almost surely, as is \(\tau_1^X\), then taking \(\lambda \to 0\) in Corollary~\ref{cor: aln222222} yields the result. 
\end{proof}
Corollary~\ref{cor: aln22222212} states that the transition probabilities of the embedded processes converge. Thus, the finite-dimensional distributions of \(\{\Ydp(n)\}\) converge, and if the space \(\mathcal K\times \calS\) is finite, then the sequence of distributions of \(\{\Ydp(n)\}\) is tight. Thus, we can establish the convergence in distribution of \(\{\Ydp(n)\}\) and \(\{\bs X(\tau_n^X)\}\).

@@

\section{Convergence of the QBD-RAP scheme}\label{sec: local to global}
This section is dedicated to proving a global convergence results of the QBD-RAP approximation scheme to the fluid queue. Ultimately, we prove the weak convergence (in space and time) of the QBD-RAP approximation scheme to the distribution of the fluid queue. This is done in stages. First, by considering the Laplace transform with respect to time of the distribution of the QBD-RAP \emph{at the time of the \(n\)th orbit restart epoch}, \(\tau_n\). Second, considering the Laplace transform with respect to time of the distribution of the QBD-RAP \emph{between} the \(n\)th and \((n+1)\)th orbit restart epoch. Third, summing over the number of orbit restart epochs, \(n\), and via the Dominated Convergence Theorem, we claim a convergence of the Laplace transforms with respect to time of the QBD-RAP and fluid queue. Lastly, we apply the Extended Continuity Theorem for Laplace transforms \cite[Chapter XIII, Theorem 2a]{feller1957} to claim a weak convergence (in space and time) of the QBD-RAP approximation scheme to the fluid queue.

@@

% Let \(\{\tau_n^X\}_{n\geq 0}\), be the sequence of (stopping) times with \(\tau_0^X=0\), and 
% \[\tau_{n+1}^X = \min\left\{\begin{array}{c}\inf\left\{t>\tau_n^X\mid X(t)=y_{\ell}, \ell\in\mathcal K\right\}, \\ \inf\left\{t>\tau_n^X \mid X(t) \neq 0, X(0)=0\right\}, \\ \inf\left\{t>\tau_n^X \mid X(t) \neq y_{K+1}, X(0)=y_{K+1}\right\} \end{array} \right\}.\]
% For \(n\geq 1\), \(\tau_n^X\) is the time at which \(X(t)\) either changes band, or hits a boundary, or the process leaves a boundary, for the \(n\)th time. 
The idea for the analysis of the QBD-RAP at the \(n\)th orbit restart epoch is to partition the distribution of the QBD-RAP on the phase and level at the times \(\tau_1^{(p)}\) and \(\tau_2^{(p)},...,\tau_{n-1}^{(p)}\) and then use the strong Markov property to write the expression in terms of the distributions of the QBD-RAP at time \(\tau_k^{p}\) given the distribution of the QBD-RAP at time \(\tau_{k-1}^{(p)}\), \(k=1,...,n\). The distribution at time \(\tau_1^{(p)}\) depends on the initial condition, so we treat it separately and use Corollary~\ref{cor: aln222} to claim convergence to the fluid queue. By time-homogeneity, the distributions of the QBD-RAP at times \(\tau_k^{p}\) given the position of the QBD-RAP at time \(\tau_{k-1}^{(p)}\) is equal to the distribution of the QBD-RAP at time \(\tau_1^{(p)}\) given an initial distribution of the QBD-RAP. Hence, we may also use Corollary~\ref{cor: aln222} to claim convergence to the fluid queue for each of these distributions. Putting all the elements together yields the convergence at the \(n\)th orbit restart epoch.

@@

Thus, returning to (\ref{eqn: 161222}), taking the limit as \(p\to\infty\), and using the convergence established in (\ref{eqn: aMMMMM}) and (\ref{eqn: lim 12}), then 
\begin{align}
	&\lim_{p\to\infty}\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}\mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda \nonumber
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1},\bs\alpha, j_{m-1})) \nonumber 
	%
	\\ &=\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}\lim_{p\to\infty} \mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1}, \bs\alpha,
	 	 j_{m-1}) ),
	 \label{eqn: 161222b}
\end{align}
where we may swap the limit and the sums as they are finite, and we can swap the limit and the product since all the limits exist and the product is finite. Substituting the limits (\ref{eqn: lim 12}) into (\ref{eqn: 161222b}) gives 
\begin{align}
	&\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}} \prod_{m=2}^{n}\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m}+1(j_{m}\in\mathcal S_-)}, j_m), \tau_{m}^X\leq E^\lambda\mid \nonumber
            	\\&\qquad\qquad  \bs X(\tau_{m-1}^X)=(y_{\ell_{m-1}+1(j_{m-1}\in\mathcal S_-)},j_{m-1}),\tau_{m-1}^X\leq E^\lambda),\nonumber
		%
		\\&= \mathbb P(\bs X(\tau_n^X) = (y_{\ell+1(j_{n}\in\mathcal S_-)}, 
		j_n), \tau_{n}^X\leq E^\lambda \mid \bs X(0)=(y_{\ell_{1}+1(j_{1}\in\mathcal S_-)},
		j_{1}), 
		\tau_1^X\leq E^\lambda),
\end{align}
by the strong Markov property of the fluid queue and the Law of total probability.

@@

Hence, we have shown the following result 
\begin{lem}\label{lem: LAkAKFnvnb mav h}
	For \(\ell,\ell_0\in\mathcal K\), \(i,j\in\calS\), \(n\geq 0\), then, as \(p\to\infty\), 
	\begin{align} 
		&\int_{t=0}^\infty e^{-\lambda t}\int_{x\in\calD_{\ell,j}}\mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x, j), t\in\mathcal T_n^{(p)} \mid  \nonumber 
		\bs Y(0) = \bs y_0)\psi(x)\wrt t \nonumber
		%
		\\&\to\int_{t=0}^\infty e^{-\lambda t}  \int_{x\in\calD_{\ell,j_n}}\mathbb P(\bs X(t)\in(\wrt x, j), t\in\mathcal T_n^{X} 
		\mid \bs X(0)=(x_0,i))\psi(x)\wrt t.
	\end{align}
\end{lem}

@@

	Suppose that the phase at time \(\tau_{n-1}\) is \(i\in\mathcal S_+\) and that at time \(\tau_{n-1}\) the QBD-RAP is not at a boundary. The arguments for an initial phase \(i\in\mathcal S_-\) are analogous. For an orbit restart epochs to occur, either; 
	\begin{enumerate}
		\item the QBD-RAP remains in phase \(i\) until the orbit restart epoch occurs, or
		\item the QBD-RAP changes phase before there is an orbit restart epoch, after which the orbit restart epoch occurs eventually. 
	\end{enumerate}

>>>>

%!TEX root = ../thesis.tex
\chapter{Global convergence results}\label{ch: global results}
In this chapter we prove convergence results which build on the main results of Chapter~\ref{sec: conv}. We consider the discrete-time embedded processes formed by observing the QBD-RAP at the orbit restart epochs and by observing the fluid queue at the hitting times of the level process on the points \(\{y_\ell\}\), which are the boundaries of the intervals \(\{\calD_\ell\}\). In Corollary~\ref{cor: aln22222212} we prove that the transition probabilities of the embedded process of the QBD-RAP converge those of the embedded process of the fluid queue. In Corollary~\ref{cor: short cor} we prove that the distribution of the sojourn time of the QBD-RAP in a given level converges to the distribution of the sojourn time of the fluid queue in the corresponding interval. In Theorem~\ref{thm: big thm}, we state global results on the weak convergence (in space and time) of the QBD-RAP approximation scheme to the fluid queue.

@@

Consider the embedded process formed by observing the QBD-RAP at the orbit restart epochs. Let \(\tau_0^{(p)}=0\), and
\[\tau_{n}^{(p)} = \inf\left\{t\geq \tau_{n-1}^{(p)} \mid L^{(p)}(t)\neq L^{(p)}(\tau_{n-1}^{(p)}), \mbox{or \(\{\bs Y(t)\}\) hits a boundary}\right\},\]
be orbit restart epochs. These are the (stopping) times at which the level process of the QBD-RAP, \(\{L^{(p)}(t)\}\), changes, or the boundary is hit, or, if the process is at the boundary, the process leaves the boundary. To simplify notation, we may drop the superscript \(p\) where it is not explicitly needed. Further, let \(\{\Ydp(n)\}_{n\geq 0, n \in \mathbb Z} = \{(L^{(p)}(\tau_n^{(p)}),\varphi(\tau_n^{(p)}))\}_{n\geq 0, n \in \mathbb Z}\) be the level and phase of the discrete-time process embedded at the orbit restart epochs. The subscript \(\bs \alpha \) refers to the fact that \(\bs A^{(p)}(\tau_n^{(p)})=\bs \alpha^{(p)}\) for \(n\geq 1\), unless the process is temporarily absorbed in a sticky boundary, in which case \(\bs A^{(p)}(\tau_n^{(p)})=1\). The process \(\{\Ydp(n)\}_{n\geq 0}\) is a discrete-time Markov chain, which is time-homogeneous for \(n\geq 1\).

@@

We have the following result on the convergence of the embedded processes \(\{\Ydp(n)\}\) and \(\{\bs X(\tau_n^X)\}\), which we also will utilise later to prove a global result.
\begin{lem}\label{cor: aln222222} For \(\ell_0\in\mathcal K,\) \(x_0\in\mathcal D_{\ell_0,i}\), \(i\in\mathcal S\), 
	then
	\begin{align}
		&\mathbb P(\Ydp(1) = (\ell(\ell_0,j),j), \tau_1^{(p)}\leq E^\lambda
            	 \mid \bs Y^{(p)}(0) = (\ell_0,\bs a_{\ell_0,i}^{(p)}(x_0),i)) \nonumber
	 	%
		\\&\to  
			\mathbb P(\bs X(\tau_1^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_1^{X}\leq E^\lambda \mid \bs X(0) = (x_0,i)),\label{eqn: lim 1}
	\end{align}
	and for \(n\geq 1\), 
	\begin{align}
		&\mathbb P(\Ydp(n+1) = (\ell(\ell_0,j),j), \tau_{n+1}^{(p)}\leq E^\lambda
            	 \mid \Ydp(n) = (\ell_0,i), \tau_n^{(p)}\leq E^\lambda) \nonumber
	 	%
		\\&\to  
			\mathbb P(\bs X(\tau_{n+1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_{n+1}^{X}\leq E^\lambda \mid \bs X(\tau_{n}^X) = (y_{\ell_0+1(i\in\calS_-)},i), \tau_n^{X}\leq E^\lambda).\label{eqn: ddddddd}
	\end{align}
	where \(\ell(\ell_0,j)\) can take values
	\begin{align}
		\ell(\ell_0,j) = \begin{cases}
			\ell_0-1, & \ell_0\in\{0,1,\dots,K+1\},\, j\in\calS_-\\
			%
			\ell_0, & \ell_0 = 0, j\in\mathcal S_+, \mbox{ or }\ell_0 = K, j\in\mathcal S_-,\\
			%
			\ell_0+1, & \ell_0\in\{-1,0,1,\dots,K\},\, j\in\calS_+.
		\end{cases}
	\end{align}
	% and 
	% \begin{align}
	% 	y(\ell,\ell_0,j) = \begin{cases}
	% 		y_{\ell_0}, & \ell=\ell_0-1,\, j\in\calS_-, \mbox{ or } \ell=\ell_0=0,\, j \in\calS_+, \\
	% 		y_{\ell_0+1}, & \ell=\ell_0+1,\, j\in\calS_+, \mbox{ or } \ell=\ell_0=K,\, j \in\calS_-.
	% 	\end{cases}
	% \end{align}
\end{lem}
\begin{proof}
The convergence for \(\ell_0\in\{-1,K+1\}\) holds trivially as the QBD-RAP and fluid queue have the same behaviour at the sticky boundary.

@@

All that is left is to prove (\ref{eqn: ddddddd}). For \(n\geq 1\), consider the transition probabilities of the embedded process from the QBD-RAP, 
\begin{align}
	&\mathbb P(\Ydp(n+1) = (\ell(\ell_0,j),j),\tau_{n+1}^{(p)}\leq E^\lambda
	\mid \Ydp(n) = (\ell_0,i),\tau_{n}^{(p)}\leq E^\lambda) \nonumber 
	\\&=\mathbb P(\Ydp(1) = (\ell(\ell_0,j),j), \tau_{1}^{(p)}\leq E^\lambda
	\mid \bs Y^{(p)}(0)=(\ell_0 ,\bs\alpha, i)), \label{eqn: aaannnn}
\end{align}
since the QBD-RAP is time-homogeneous and the exponential random variable \(E^\lambda\) is memoryless. %The probability on the right of (\ref{eqn: aaannnn}) is equal to
% \begin{align}
% 	&\mathbb P(L^{(p)}(\tau_1^{(p)}) = \ell_0-1(j\in\calS_-)+1(j\in\calS_+), \varphi(\tau_1^{(p)}) = j
% 			 \mid \bs Y^{(p)}(0) = (\ell_0 ,\bs\alpha, i)).\nonumber
% 	%  \intertext{for \(j\in\calS_+\)}
% 	%  &\mathbb P(L^{(p)}(\tau_1^{(p)}) = \ell_0-1, \varphi(\tau_1^{(p)}) = j
% 	% 		 \mid \bs Y^{(p)}(0) = \bs y_0^{(p)}) \nonumber
% \end{align}
% Thus, once again noting that \(\tau_1^{(p)}<\infty\) almost surely, then taking \(\lambda \to 0\) in 
Applying Corollary~\ref{cor: aln222} to (\ref{eqn: aaannnn}) then
\begin{align}
	&\mathbb P(\Ydp(n+1) = (\ell(\ell_0,j),j),\tau_{n+1}^{(p)}\leq E^\lambda
	\mid \Ydp(n) = (\ell_0,i),\tau_{n}^{(p)}\leq E^\lambda) \nonumber 
	\\&\to \mathbb P(\bs X(\tau_{1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_{1}^{X}\leq E^\lambda \mid \bs X(0) = (y_{\ell_0+1(i\in\calS_-)},i)).\label{eqnL sdfdfaaa}
\end{align}
Since the fluid queue is time-homogeneous, and \(E^\lambda\) memoryless, then (\ref{eqnL sdfdfaaa}) is equal to 
\begin{align}
	&\mathbb P(\bs X(\tau_{1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_{1}^{X}\leq E^\lambda \mid \bs X(\tau_{1}^X) = (y_{\ell_0+1(i\in\calS_-)},i)) \nonumber
	\\&=\mathbb P(\bs X(\tau_{n+1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j), \tau_{n+1}^{X}\leq E^\lambda \mid \bs X(\tau_{n}^X) = (y_{\ell_0+1(i\in\calS_-)},i), \tau_{n}^{X}\leq E^\lambda ),
\end{align}
which proves the result. 
\end{proof}
A direct corollary of Lemma~\ref{cor: aln222222} is the convergence of the transition probabilities of the embedded process. 
\begin{cor}\label{cor: aln22222212} For \(\ell_0\in \mathcal K,\) \(x_0\in\mathcal D_{\ell_0,i}\), \(i\in\mathcal S\), 
		then
		\begin{align}
			&\mathbb P(\Ydp(1) = (\ell(\ell_0,j),j)
					 \mid \bs Y^{(p)}(0) = (\ell_0,\bs a_{\ell_0,i}^{(p)}(x_0),i)) \nonumber
			 %
			\\&\to  
				\mathbb P(\bs X(\tau_1^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j)  \mid \bs X(0) = (x_0,i)).\label{eqn: lim 2}
		\end{align}
		and for \(n\geq 1\),  
		\begin{align}
			&\mathbb P(\Ydp(n+1) = (\ell(\ell_0,j),j) 
					 \mid \Ydp(n) = (\ell_0,i) ) \nonumber
			 %
			\\&\to  
				\mathbb P(\bs X(\tau_{n+1}^X) = (y_{\ell(\ell_0,j)+1(j\in\calS_-)}, j) \mid \bs X(\tau_{n}) = (y_{\ell_0+1(i\in\calS_-)},i) ).\label{eqn: ddddddd2}
		\end{align}
\end{cor}
\begin{proof}
	Since \(\tau_1^{(p)}<\infty\) almost surely, as is \(\tau_1^X\), then taking \(\lambda \to 0\) in Lemma~\ref{cor: aln222222} yields the result. 
\end{proof}
Corollary~\ref{cor: aln22222212} states that the transition probabilities of the embedded processes converge. Thus, the finite-dimensional distributions of \(\{\Ydp(n)\}\) converge, and if the space \(\mathcal K\times \calS\) is finite, then the sequence of distributions of \(\{\Ydp(n)\}\) is tight. Thus, by Theorem~\ref{thm: aofaa}, we establish convergence in distribution of \(\{\Ydp(n)\}\) and \(\{\bs X(\tau_n^X)\}\).

@@

\section{Convergence of the QBD-RAP scheme}\label{sec: local to global}
This section is dedicated to proving a global convergence results of the QBD-RAP approximation scheme to the fluid queue. Ultimately, we prove the weak convergence (in space and time) of the QBD-RAP approximation scheme to the distribution of the fluid queue. This is done in stages. First, by considering the Laplace transform with respect to time of the distribution of the QBD-RAP \emph{at the time of the \(n\)th orbit restart epoch}, \(\tau_n\). Second, considering the Laplace transform with respect to time of the distribution of the QBD-RAP \emph{between} the \(n\)th and \((n+1)\)th orbit restart epoch. Third, summing over the number of orbit restart epochs, \(n\), and using the Dominated Convergence Theorem, we establish a convergence of the Laplace transforms with respect to time of the QBD-RAP and fluid queue. Lastly, we apply the Extended Continuity Theorem for Laplace transforms \cite[Chapter XIII, Theorem 2a]{feller1957} to establish a weak convergence (in space and time) of the QBD-RAP approximation scheme to the fluid queue.

@@

% Let \(\{\tau_n^X\}_{n\geq 0}\), be the sequence of (stopping) times with \(\tau_0^X=0\), and 
% \[\tau_{n+1}^X = \min\left\{\begin{array}{c}\inf\left\{t>\tau_n^X\mid X(t)=y_{\ell}, \ell\in\mathcal K\right\}, \\ \inf\left\{t>\tau_n^X \mid X(t) \neq 0, X(0)=0\right\}, \\ \inf\left\{t>\tau_n^X \mid X(t) \neq y_{K+1}, X(0)=y_{K+1}\right\} \end{array} \right\}.\]
% For \(n\geq 1\), \(\tau_n^X\) is the time at which \(X(t)\) either changes band, or hits a boundary, or the process leaves a boundary, for the \(n\)th time. 
The idea for the analysis of the QBD-RAP at the \(n\)th orbit restart epoch is to partition the distribution of the QBD-RAP on the phase and level at the times \(\tau_1^{(p)}\) and \(\tau_2^{(p)},...,\tau_{n-1}^{(p)}\) and then use the strong Markov property to write the expression in terms of the distributions of the QBD-RAP at time \(\tau_k^{p}\) given the distribution of the QBD-RAP at time \(\tau_{k-1}^{(p)}\), \(k=1,...,n\). The distribution at time \(\tau_1^{(p)}\) depends on the initial condition, so we treat it separately and use Corollary~\ref{cor: aln222} to establish convergence to the fluid queue. By time-homogeneity, the distributions of the QBD-RAP at times \(\tau_k^{p}\) given the position of the QBD-RAP at time \(\tau_{k-1}^{(p)}\) is equal to the distribution of the QBD-RAP at time \(\tau_1^{(p)}\) given an initial distribution of the QBD-RAP. Hence, we may also use Corollary~\ref{cor: aln222} to establish convergence to the fluid queue for each of these distributions. Putting all the elements together yields the convergence at the \(n\)th orbit restart epoch.

@@

Thus, returning to (\ref{eqn: 161222}), taking the limit as \(p\to\infty\), and using the convergence established in (\ref{eqn: aMMMMM}) and (\ref{eqn: lim 12}), we see that  
\begin{align}
	&\lim_{p\to\infty}\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}\mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda \nonumber
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1},\bs\alpha, j_{m-1})) \nonumber 
	%
	\\ &=\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}\lim_{p\to\infty} \mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1}, \bs\alpha,
	 	 j_{m-1}) ),
	 \label{eqn: 161222b}
\end{align}
where we may swap the limit and the sums as they are finite, and we can swap the limit and the product since all the limits exist and the product is finite. Substituting the limits (\ref{eqn: lim 12}) into (\ref{eqn: 161222b}) gives 
\begin{align}
	&\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}} \prod_{m=2}^{n}\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m}+1(j_{m}\in\mathcal S_-)}, j_m), \tau_{m}^X\leq E^\lambda\mid \nonumber
            	\\&\qquad\qquad  \bs X(\tau_{m-1}^X)=(y_{\ell_{m-1}+1(j_{m-1}\in\mathcal S_-)},j_{m-1}),\tau_{m-1}^X\leq E^\lambda),\nonumber
		%
		\\&= \mathbb P(\bs X(\tau_n^X) = (y_{\ell+1(j_{n}\in\mathcal S_-)}, 
		j_n), \tau_{n}^X\leq E^\lambda \mid \bs X(0)=(y_{\ell_{1}+1(j_{1}\in\mathcal S_-)},
		j_{1}), 
		\tau_1^X\leq E^\lambda),
\end{align}
by the strong Markov property of the fluid queue and the Law of Total Probability.

@@

Hence, we have shown
\begin{lem}\label{lem: LAkAKFnvnb mav h}
	For \(\ell,\ell_0\in\mathcal K\), \(i,j\in\calS\), \(n\geq 0\), then, as \(p\to\infty\), 
	\begin{align} 
		&\int_{t=0}^\infty e^{-\lambda t}\int_{x\in\calD_{\ell,j}}\mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x, j), t\in\mathcal T_n^{(p)} \mid  \nonumber 
		\bs Y(0) = \bs y_0)\psi(x)\wrt t \nonumber
		%
		\\&\to\int_{t=0}^\infty e^{-\lambda t}  \int_{x\in\calD_{\ell,j_n}}\mathbb P(\bs X(t)\in(\wrt x, j), t\in\mathcal T_n^{X} 
		\mid \bs X(0)=(x_0,i))\psi(x)\wrt t.
	\end{align}
\end{lem}

@@

	Suppose that the phase at time \(\tau_{n-1}\) is \(i\in\mathcal S_+\) and that at time \(\tau_{n-1}\) the QBD-RAP is not at a boundary. The arguments for an initial phase \(i\in\mathcal S_-\) are analogous. For an orbit restart epoch to occur, either; 
	\begin{enumerate}
		\item the QBD-RAP remains in phase \(i\) until the orbit restart epoch occurs, or
		\item the QBD-RAP changes phase before there is an orbit restart epoch, after which the orbit restart epoch occurs eventually. 
	\end{enumerate}
